Incentivizing Exploration with Unbiased History

### 2018-11-01 3level.tex
update figures
remove "randomness" in the policy description, our info graph is deterministic and public knowledge
T_G -> alex's macro

The policy consists of three phases, each of which corresponds to a
level (see Figure~\ref{fig:3level}).  In the first level, the policy
performs the first round of exploration over the first
$(S\cdot T_1\cdot T_G)$ agents, where $T_1 = T^{4/7}\log^{-1/7}(T)$
and $S = 2^{10}\log(T)$. In particular, the policy randomly partitions
the agents into $S$ groups such that each group consists of $T_1$ runs
of \ALGG with $T_G$ rounds. In the second level, the policy performs
further exploration on the next $(S\cdot T_2)$ agents by incorporating
data collected in the first level, where
$T_2 = T^{6/7}\log^{-5/7}(T)$. The agents are again partitioned into
$S$ groups such that the agents in the $s$-th group are shown the same
sub-history from the $s$-th group in the first level. In the third
level, the policy exploits by showing all remaining agents the entire
history from the first two levels. \nicomment{This comment applies to the 2level too; why not allow the guys within the last level see each other?  Seems like this would still work but be more of a headache to prove -- would have to argue the empirical means can't move around too much in the sub-terminal levels, but it makes a big qualitative difference because now everyone sees a vanishingly small fraction of the history whereas with this modification a fraction approaching 1 of the people see a fraction approaching 1 of the history.} \jmcomment{To do it for the last level is actually easy. It would be headache to do it for the second level as we want to prove anti-concentration in the second level. On the other hand, we have the property that agents see $1/polylog$ fraction of history in our final result for $l$-level. A different point of view is that, seeing each other requires more interaction, our policy has the nice property that the interaction is very minimal except the initial greedy runs.}

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \filldraw[fill=green!20!white]
 (0,4)--(10,4)--(10,5)--(0,5)--cycle;
 \foreach \x in {0,3,8}
 {
 \filldraw[fill=blue!20!white]
 (\x+0,2)--(\x+2,2)--(\x+2,3)--(\x+0,3)--cycle;
 \draw[dashed] (\x+1,3)--(5,4);
 \filldraw[fill=red!20!white]
 (\x+0,0)--(\x+2,0)--(\x+2,1)--(\x+0,1)--cycle;
 \draw[dashed] (\x+1,1)--(\x+1,2);
 \draw[dashed] (\x+0.2,1)--(\x+1,2);
 \draw[dashed] (\x+0.6,1)--(\x+1,2);
 \draw[dashed] (\x+1.4,1)--(\x+1,2);
 \draw[dashed] (\x+1.8,1)--(\x+1,2);
 \draw[dashed] (\x+0.4,0)--(\x+0.4,1); 
 \draw[dashed] (\x+0.8,0)--(\x+0.8,1); 
 \draw[dashed] (\x+1.2,0)--(\x+1.2,1); 
 \draw[dashed] (\x+1.6,0)--(\x+1.6,1);  
 \node at(\x+1,2.5){$T_2$};
 \node at(\x+0.2, 0.5){$\GdT$};
 \node at(\x+0.6, 0.5){$\cdot$};
 \node at(\x+1.0, 0.5){$\cdot$};
 \node at(\x+1.4, 0.5){$\cdot$};
 \node at(\x+1.8, 0.5){$\GdT$};
 %\node at(\x+1,0.5){$T_1 \cdot \GdT$}; 
 \draw [decorate,decoration={brace,amplitude=10pt},xshift=0pt,yshift=0pt] (\x+2,-0.2) -- (\x+0,-0.2) node [black,midway,yshift=-0.6cm] {$T_1$ runs};
 }
  \node at(5,4.5){$T -S(T_1 \cdot \GdT + T_2)$};
  \node at (6,0.5){$\cdots$};
  \node at (7,0.5){$\cdots$};
  \node at (6,2.5){$\cdots$};
  \node at (7,2.5){$\cdots$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \node at(-1,4.5){\textbf{Levle 3}};
  \draw[->] (11,0)--(11,5);
  \node at(11.5,2.5)[ rotate=90]{Time};

@@

\end{tikzpicture}
\caption{Structure of the information graph for the 3-level
  Policy. Each red box in level 1 corresponds to $T_1$ \ALGG paths of
  length $T_G$. The sub-history of each red box is then aggregated and
  sent to a corresponding purple box of agents in level 2. Then the
  entire history of levels 1 and 2 is aggregated and shown to all
  agents in level 3.}
\label{fig:3level}
\end{figure}
% \swcomment{check the figure caption above. can we index the indicate
%   there are $S$ groups in the figure?}

@@

\begin{lemma}[Concentration of first-level number of pulls.]\label{3levelw1}
  Let $W_1$ be the event that for all groups $s\in [S]$ and arms
  $a\in \{1, 2\}$, the number of arm $a$ pulls in the $s$-th
  first-level group is in the range of
  $$
  \left[q_a T_1- \GdT \sqrt{T_1\log(T)}, q_a T_1 + \GdT \sqrt{T_1\log(T)}\right],
  $$
  where $q_a$ is the expected number of arm $a$ pulls in a $\ALGG$ run
  of length $T_G$. Then $\Pr[W_1] \geq 1- \frac{4S}{T^2}$.
\end{lemma}

@@

\paragraph{Wrapping up: proof of \Cref{thm:3level}. } In negligible
gap case, the stated regret bound holds regardless of the sequence of
chosen arms. In the large gap case, the regret only comes from the
first level, which is bounded
by $S T_G T_1 = O(T^{4/7} \log^{6/7}(T))$. In the intermediate cases of
both medium and small gaps, it suffices to bound the regret from the
first and second levels, so
\[
\reg(T) \leq (S T_G T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
+ \sqrt{\frac{4\log(T)}{q_2T_1}}\right) = O(T^{4/7} \log^{6/7}(T)).
\]
Therefore, we obtain the stated regret bound in all cases.

>>>>

The policy consists of three phases, each of which corresponds to a
level (see Figure~\ref{fig:3level}).  In the first level, the policy
performs the first round of exploration over the first
$(S\cdot T_1\cdot \GdT)$ agents, where $T_1 = T^{4/7}\log^{-1/7}(T)$
and $S = 2^{10}\log(T)$. In particular, the policy partitions
the agents into $S$ groups such that each group consists of $T_1$ runs
of \ALGG with $\GdT$ rounds. In the second level, the policy performs
further exploration on the next $(S\cdot T_2)$ agents by incorporating
data collected in the first level, where
$T_2 = T^{6/7}\log^{-5/7}(T)$. The agents are again partitioned into
$S$ groups such that the agents in the $s$-th group are shown the same
sub-history from the $s$-th group in the first level. In the third
level, the policy exploits by showing all remaining agents the entire
history from the first two levels. \nicomment{This comment applies to the 2level too; why not allow the guys within the last level see each other?  Seems like this would still work but be more of a headache to prove -- would have to argue the empirical means can't move around too much in the sub-terminal levels, but it makes a big qualitative difference because now everyone sees a vanishingly small fraction of the history whereas with this modification a fraction approaching 1 of the people see a fraction approaching 1 of the history.} \jmcomment{To do it for the last level is actually easy. It would be headache to do it for the second level as we want to prove anti-concentration in the second level. On the other hand, we have the property that agents see $1/polylog$ fraction of history in our final result for $l$-level. A different point of view is that, seeing each other requires more interaction, our policy has the nice property that the interaction is very minimal except the initial greedy runs.}

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \filldraw[fill=green!20!white]
 (0,4)--(10,4)--(10,5)--(0,5)--cycle;
 \foreach \x in {0,3,8}
 {
 \filldraw[fill=blue!20!white]
 (\x+0,2)--(\x+2,2)--(\x+2,3)--(\x+0,3)--cycle;
 \draw (\x+1,3)--(5,4);
 \filldraw[fill=red!20!white]
 (\x+0,0)--(\x+2,0)--(\x+2,1)--(\x+0,1)--cycle;
 \draw (\x+1,1)--(\x+1,2);
 \draw(\x+0.2,1)--(\x+1,2);
 \draw(\x+0.6,1)--(\x+1,2);
 \draw(\x+1.4,1)--(\x+1,2);
 \draw(\x+1.8,1)--(\x+1,2);
 \draw(\x+0.4,0)--(\x+0.4,1); 
 \draw(\x+0.8,0)--(\x+0.8,1); 
 \draw (\x+1.2,0)--(\x+1.2,1); 
 \draw(\x+1.6,0)--(\x+1.6,1);  
 \node at(\x+1,2.5){$T_2$};
 \node at(\x+0.2, 0.5){$\GdT$};
 \node at(\x+0.6, 0.5){$\cdot$};
 \node at(\x+1.0, 0.5){$\cdot$};
 \node at(\x+1.4, 0.5){$\cdot$};
 \node at(\x+1.8, 0.5){$\GdT$};
 %\node at(\x+1,0.5){$T_1 \cdot \GdT$}; 
 \draw [decorate,decoration={brace,amplitude=10pt},xshift=0pt,yshift=0pt] (\x+2,-0.2) -- (\x+0,-0.2) node [black,midway,yshift=-0.6cm] {$T_1$ runs};
 }
  \node at(5,4.5){$T -S(T_1 \cdot \GdT + T_2)$};
  \node at (6,0.5){$\cdots$};
  \node at (7,0.5){$\cdots$};
  \node at (6,2.5){$\cdots$};
  \node at (7,2.5){$\cdots$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \node at(-1,4.5){\textbf{Levle 3}};
  \draw[->] (11,0)--(11,5);
  \node at(11.5,2.5)[ rotate=90]{Time};

@@

\end{tikzpicture}
\caption{Structure of the information graph for the 3-level
  Policy. Each red box in level 1 corresponds to $T_1$ \ALGG paths of
  length $\GdT$. The sub-history of each red box is then aggregated and
  sent to a corresponding purple box of agents in level 2. Then the
  entire history of levels 1 and 2 is aggregated and shown to all
  agents in level 3.}
\label{fig:3level}
\end{figure}
% \swcomment{check the figure caption above. can we index the indicate
%   there are $S$ groups in the figure?}

@@

\begin{lemma}[Concentration of first-level number of pulls.]\label{3levelw1}
  Let $W_1$ be the event that for all groups $s\in [S]$ and arms
  $a\in \{1, 2\}$, the number of arm $a$ pulls in the $s$-th
  first-level group is in the range of
  $$
  \left[q_a T_1- \GdT \sqrt{T_1\log(T)}, q_a T_1 + \GdT \sqrt{T_1\log(T)}\right],
  $$
  where $q_a$ is the expected number of arm $a$ pulls in a $\ALGG$ run
  of length $\GdT$. Then $\Pr[W_1] \geq 1- \frac{4S}{T^2}$.
\end{lemma}

@@

\paragraph{Wrapping up: proof of \Cref{thm:3level}. } In negligible
gap case, the stated regret bound holds regardless of the sequence of
chosen arms. In the large gap case, the regret only comes from the
first level, which is bounded
by $S \GdT T_1 = O(T^{4/7} \log^{6/7}(T))$. In the intermediate cases of
both medium and small gaps, it suffices to bound the regret from the
first and second levels, so
\[
\reg(T) \leq (S \GdT T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
+ \sqrt{\frac{4\log(T)}{q_2T_1}}\right) = O(T^{4/7} \log^{6/7}(T)).
\]
Therefore, we obtain the stated regret bound in all cases.

### 2018-11-01 3levelproofs.tex
check in often!
some appendix edits
T_G -> alex's macro

\subsection{Clean Events}

@@

\subsection{Case Analysis under Clean Events}
Now we assume the intersection of clean events $W$ happens. We will
first provide some helper lemmas for our case analysis.

@@

Now consider the agents in the third level group. Recall $\bar{\mu}_a$
is the empirical mean of arm $a$ in the history they see. We have
\[
\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{Sq_1T_1}} - \sqrt{\frac{4\log(T)}{Sq_2T_1}} \geq  \sqrt{\frac{4\log(T)}{q_1T_1}} 
+ \sqrt{\frac{4\log(T)}{q_2T_1}}.
\]
Similarly as above, by Assumption \ref{ass:embehave}, we know
$\hat{\mu}_1^t - \hat{\mu}_2^t > 0$ for any agent $t$ in the third
level. Therefore, the agents in the third-level group will all pull
arm 1.  \OMIT{Therefore the expected regret is at most
  $S T_G T_1 = O(T^{4/7} \log^{6/7}(T))$.}
\end{proof}

\begin{proof}[Proof of Lemma~\ref{3levelmedium} (Medium gap case)]
  % $2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} +
  %   \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \leq \mu_1-\mu_2 <
  % 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} +
  %   \sqrt{\frac{4\log(T)}{q_2T_1}}\right)$. 
  Recall $\bar{\mu}_a$ is
  the empirical mean of arm $a$ in the first two levels. We have
\[
\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{Sq_1T_1}} - \sqrt{\frac{4\log(T)}{Sq_2T_1}} \geq  \sqrt{\frac{4\log(T)}{Sq_1T_1}} 
+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}.
\]
For any agent $t$ in the third level, by Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1 - \bar{\mu}_2 - \frac{c_m}{\sqrt{Sq_1T_1/2}} - \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
&\geq  \sqrt{\frac{4\log(T)}{Sq_1T_1}} + \sqrt{\frac{4\log(T)}{Sq_2T_1}}- \frac{c_m}{\sqrt{Sq_1T_1/2}} - \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
 &> 0.
\end{align*}
So we know agents in the third-level group will all pull arm 1. \OMIT{Therefore the expected regret is at most 
\[
(S T_G T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
+ \sqrt{\frac{4\log(T)}{q_2T_1}}\right) = O(T^{4/7} \log^{6/7}(T))
\]
}
\end{proof}

\begin{proof}[Proof of Lemma~\ref{3levelsmallcase} (Small gap case)]
  % $ 3\sqrt{\frac{2\log(T)}{T_2}} < \mu_1-\mu_2 <
  % 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} +
  %   \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right)$.  
  In this case, we need both arms to be pulled at least $T_2$ rounds
  in the second level. For every arm $a$, consider the $s_a$-th
  second-level group, with $s_a$ given by Lemma~\ref{lem:luck}. We
  have
\begin{align*}
\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} &> \mu_a + \frac{1}{4\sqrt{q_aT_1}} -\mu_{3-a} +\frac{1}{4\sqrt{q_{3-a}T_1}} \\
&> \frac{1}{4\sqrt{q_1T_1}}+ \frac{1}{4\sqrt{q_2T_1}} - 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \\
&\geq \frac{1}{8\sqrt{q_1T_1}}+ \frac{1}{8\sqrt{q_2T_1}}.
\end{align*}
For any agent $t$ in the $s_a$-th second-level group, by Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &>\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} - \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
&\geq   \frac{1}{8\sqrt{q_1T_1}}+ \frac{1}{8\sqrt{q_2T_1}}- \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
 &> 0.
\end{align*}
So we know agents in the $s_a$-th second-level group will all pull arm $a$. Therefore in the first two levels, both arms are pulled at least $T_2$ times. Now consider the third-level. We have
\[
\bar{\mu}_1 - \bar{\mu}_2  \geq \mu_1 -\mu_2 - 2\sqrt{\frac{2\log(T)}{T_2}} \geq \sqrt{\frac{2\log(T)}{T_2}}.
\]
Similarly as above, by Assumption \ref{ass:embehave}, we know $\hat{\mu}_1^t - \hat{\mu}_2^t > 0$ for any agent $t$ in the third level. So we know agents in the third-level group will all pull arm 1.\OMIT{
Therefore the expected regret is at most 
\[
(S T_G T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \leq O(T^{4/7} \log^{6/7}(T))
\]
}
\end{proof}

>>>>

\subsection{Events}

@@

\subsection{Case Analysis}
Now we assume the intersection $W$ of events $W_1,\cdots,W_4$ happens. We will
first provide some helper lemmas for our case analysis.

@@

Now consider the agents in the third level group. Recall $\bar{\mu}_a$
is the empirical mean of arm $a$ in the history they see. We have
\[
\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{Sq_1T_1}} - \sqrt{\frac{4\log(T)}{Sq_2T_1}} \geq  \sqrt{\frac{4\log(T)}{q_1T_1}} 
+ \sqrt{\frac{4\log(T)}{q_2T_1}}.
\]
Similarly as above, by Assumption \ref{ass:embehave}, we know
$\hat{\mu}_1^t - \hat{\mu}_2^t > 0$ for any agent $t$ in the third
level. Therefore, the agents in the third-level group will all pull
arm 1.  \OMIT{Therefore the expected regret is at most
  $S \GdT T_1 = O(T^{4/7} \log^{6/7}(T))$.}
\end{proof}

\begin{proof}[Proof of Lemma~\ref{3levelmedium} (Medium gap case)]
  % $2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} +
  %   \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \leq \mu_1-\mu_2 <
  % 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} +
  %   \sqrt{\frac{4\log(T)}{q_2T_1}}\right)$. 
  Recall $\bar{\mu}_a$ is
  the empirical mean of arm $a$ in the first two levels. We have
\[
\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{Sq_1T_1}} - \sqrt{\frac{4\log(T)}{Sq_2T_1}} \geq  \sqrt{\frac{4\log(T)}{Sq_1T_1}} 
+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}.
\]
For any agent $t$ in the third level, by Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1 - \bar{\mu}_2 - \frac{c_m}{\sqrt{Sq_1T_1/2}} - \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
&\geq  \sqrt{\frac{4\log(T)}{Sq_1T_1}} + \sqrt{\frac{4\log(T)}{Sq_2T_1}}- \frac{c_m}{\sqrt{Sq_1T_1/2}} - \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
 &> 0.
\end{align*}
So we know agents in the third-level group will all pull arm 1. \OMIT{Therefore the expected regret is at most 
\[
(S \GdT T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
+ \sqrt{\frac{4\log(T)}{q_2T_1}}\right) = O(T^{4/7} \log^{6/7}(T))
\]
}
\end{proof}

\begin{proof}[Proof of Lemma~\ref{3levelsmallcase} (Small gap case)]
  % $ 3\sqrt{\frac{2\log(T)}{T_2}} < \mu_1-\mu_2 <
  % 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} +
  %   \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right)$.  
  In this case, we need both arms to be pulled at least $T_2$ rounds
  in the second level. For every arm $a$, consider the $s_a$-th
  second-level group, with $s_a$ given by Lemma~\ref{lem:luck}. We
  have
\begin{align*}
\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} &> \mu_a + \frac{1}{4\sqrt{q_aT_1}} -\mu_{3-a} +\frac{1}{4\sqrt{q_{3-a}T_1}} \\
&> \frac{1}{4\sqrt{q_1T_1}}+ \frac{1}{4\sqrt{q_2T_1}} - 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \\
&\geq \frac{1}{8\sqrt{q_1T_1}}+ \frac{1}{8\sqrt{q_2T_1}}.
\end{align*}
For any agent $t$ in the $s_a$-th second-level group, by Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &>\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} - \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
&\geq   \frac{1}{8\sqrt{q_1T_1}}+ \frac{1}{8\sqrt{q_2T_1}}- \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
 &> 0.
\end{align*}
So we know agents in the $s_a$-th second-level group will all pull arm $a$. Therefore in the first two levels, both arms are pulled at least $T_2$ times. Now consider the third-level. We have
\[
\bar{\mu}_1 - \bar{\mu}_2  \geq \mu_1 -\mu_2 - 2\sqrt{\frac{2\log(T)}{T_2}} \geq \sqrt{\frac{2\log(T)}{T_2}}.
\]
Similarly as above, by Assumption \ref{ass:embehave}, we know $\hat{\mu}_1^t - \hat{\mu}_2^t > 0$ for any agent $t$ in the third level. So we know agents in the third-level group will all pull arm 1.\OMIT{
Therefore the expected regret is at most 
\[
(S \GdT T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \leq O(T^{4/7} \log^{6/7}(T))
\]
}
\end{proof}

### 2018-11-01 app-warmup.tex
T_G -> alex's macro

\begin{proof}[Proof of Theorem~\ref{thm:2level}]
  We will set $T_1$ later in the proof, depending on whether the gap
  parameter $\Delta$ is known. For now, we just need to know we will
  make $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$. Since this policy is
  agnostic to the indices of the arms, we assume w.l.o.g. that arm 1
  has the highest mean.

@@

% \begin{itemize}
  \OMIT{\paragraph{Concentration of the number of arm $a$ pulls in the first
    level.}
By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.}
  Define $W_1^a$ to be the event that the number of arm $a$ pulls in
  the first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.
  \swedit{As long as we set $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$,
    this implies that the number of arm $a$ pulls is then at least
    $q_a T_1/2$.}
\OMIT{  By Chernoff bound,
  \[
    \Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
  \]
}
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By Lemma~\ref{lem:t1runs}, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\OMIT{\paragraph{Concentration of the empirical mean of arm $a$ pulls
    in the first level.}}  Next, we show that the empirical mean of
each arm $a$ is close to the true mean. To facilitate our reasoning,
let us imagine there is a tape of length $T$ for each arm $a$, with
each cell containing an independent draw of the realized reward from
the distribution $\cD_a$. Then for each arm $a$ and any $N\in [T]$, we
can think of the sequence of the first $N$ realized rewards of $a$
coming from the prefix of $N$ cells in its reward tape. Define
$W^{a,t}_2$ to be the event that the empirical mean of the first $t$
\swedit{realized rewards in the tape} of arm $a$ is at most
$\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$ to be the
intersection of these events (i.e.  $\bigcap_{a,t} W^{a,t}_2$).  By
Chernoff bound,\swcomment{$t$ may be confusing here}
\[
\Pr[W^{a,t}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
\]
By union bound,
\[
\Pr[W_2] \geq 1 - KT \cdot \frac{2}{T^4} \geq 1 - \frac{2}{T}.
\]

>>>>

\begin{proof}[Proof of Theorem~\ref{thm:2level}]
  We will set $T_1$ later in the proof, depending on whether the gap
  parameter $\Delta$ is known. For now, we just need to know we will
  make $T_1 \geq \frac{4(\GdT)^2}{(\GdP)^2}\log(T)$. Since this policy is
  agnostic to the indices of the arms, we assume w.l.o.g. that arm 1
  has the highest mean.

@@

% \begin{itemize}
  \OMIT{\paragraph{Concentration of the number of arm $a$ pulls in the first
    level.}
By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.}
  Define $W_1^a$ to be the event that the number of arm $a$ pulls in
  the first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.
  \swedit{As long as we set $T_1 \geq \frac{4(\GdT)^2}{(\GdP)^2}\log(T)$,
    this implies that the number of arm $a$ pulls is then at least
    $q_a T_1/2$.}
\OMIT{  By Chernoff bound,
  \[
    \Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
  \]
}
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By Lemma~\ref{lem:t1runs}, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\OMIT{\paragraph{Concentration of the empirical mean of arm $a$ pulls
    in the first level.}}  Next, we show that the empirical mean of
each arm $a$ is close to the true mean. To facilitate our reasoning,
let us imagine there is a tape of length $T$ for each arm $a$, with
each cell containing an independent draw of the realized reward from
the distribution $\cD_a$. Then for each arm $a$ and any $N\in [T]$, we
can think of the sequence of the first $N$ realized rewards of $a$
coming from the prefix of $N$ cells in its reward tape. Define
$W^{a,t}_2$ to be the event that the empirical mean of the first $t$
\swedit{realized rewards in the tape} of arm $a$ is at most
$\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$ to be the
intersection of these events (i.e.  $\bigcap_{a,t} W^{a,t}_2$).  By
Chernoff bound,\swcomment{$t$ may be confusing here}
\[
\Pr[W^{a,t}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
\]
By union bound,
\[
\Pr[W_2] \geq 1 - KT \cdot \frac{2}{T^4} \geq 1 - \frac{2}{T}.
\]
